---
title: "Homework 10 (presentation)"
author: "Akira Sasaki"
date: "11/19/2017"
output:
  beamer_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

## Stock Market Index Model for Election Forcasting

The 2016 US presidential election result was a huge surprise to all people as the outcome was totally different from what the majority of pollsters and media had forecasted. However, there was one interesting indicator that was free from any intentional bias and that could have been used to predict Trump’s win before the election had taken place; stock market index. According to Long (2016), the S&P 500 index performance during the latest three months prior to the election indicated that Trump would likely win against Hilary at the election. The mechanism is as follows. Firstly, the stock index is tracked during the last three before the election month. Then, the ups-and-downs of the market during the period are analyzed. If the index rose from the beginning at the end of the period, the incumbent governing parties are predicted to win the election. If it shows the opposite trend, the incumbent party will lose. The underlying theory is that “if the economy is growing and people think the good times will continue, they are likely to want to stick with the same presidential party. If they are fearful, stocks tend to fall, and voters want new leadership” (Long, 2016).


## Research Design

1. Model setting
2. The length of the period of tracking the stock market
3. When to start tracking the stock market index
4. Actual economy vs. perception
5. Potential of Conservative's advantage

## CDAX quarterly growth vs. GDP quarterly growth

```{r setting, include=FALSE, echo=FALSE}
library(foreign) #read foreign file objects
install.packages("dplyr", repos = "https://cran.rstudio.com/")
library(dplyr) #manipulate data
install.packages("ggplot2", repos = "https://cran.rstudio.com/")
library(ggplot2) #plot results
install.packages("psych", repos = "https://cran.rstudio.com/")
library(psych) #create summary statistics
library(plyr) #tools for splitting, qpplying and combining data
require(haven)
library(lubridate)
install.packages("repmis", repos = "https://cran.rstudio.com/")
library(repmis)
library(data.table)
library(magrittr)
install.packages("stargazer", repos = "https://cran.rstudio.com/")
library(stargazer)
install.packages("broom", repos = "https://cran.rstudio.com/")
library(broom)
install.packages("arm", repos = "https://cran.rstudio.com/")
library(arm)
install.packages("devtools", repos = "https://cran.rstudio.com/")
devtools::install_github("rstudio/rmarkdown")

CDAX <- read.csv("~/Stock-Market-Model/^CDAXX.csv")
CDAX$Date <- ymd(as.character(CDAX$Date))
CDAX$X3M_before <- ymd(as.character(CDAX$X3M_before))
CDAX$X6M_before <- ymd(as.character(CDAX$X6M_before))
CDAX$X9M_before <- ymd(as.character(CDAX$X9M_before))
CDAX$X12_before <- ymd(as.character(CDAX$X12_before))
library(readr)
CDAX_quarterly <- read_csv("~/Stock-Market-Model/CDAX_quarterly.csv")
CDAX_quarterly$Date <- ymd(as.character(CDAX_quarterly$Date))
GFE_Kayser <- read_dta('~/Stock-Market-Model/BundestagForecastReplicationData.dta')
GDP <- read_csv("~/Stock-Market-Model/GDP.csv")
GDP$Date <- ymd(as.character(GDP$DATE))
GFE_Kayser$Date <- as.Date(GFE_Kayser$date, "%d.%m.%Y")
```

```{r plot CDAX_GDP, include=TRUE, echo=TRUE, size="tiny"}
par(mar = c(5,5,2,5))
with(CDAX_quarterly, plot(as.Date(Date), stock_gr, type="l", col="red3", 
xlab="Year", ylab= "CDAX quarterly growth (%)"), ylim=c(-30, 30))
par(new = T)
with(GDP, plot(as.Date(Date), GDP_growth, type="l", axes=F, col="blue3", xlab="Year", ylab=NA, cex=1.2))
axis(side = 4)
mtext(side = 4, line = 3, 'GDP quarterly growth (%)')
legend("topleft",
legend=c("CDAX quarterly growth (%)", "GDP quarterly growth (%)"),
lty=1:1, cex=0.50, col=c("red3", "blue3"))
CDAX_GDP <- merge(CDAX_quarterly, GDP, by = "Date", all = TRUE)
```

## Interim Conclusion

According to a close analysis, it seems CDAX leads GDP by 1 to 2 quarters (3 months to 6 months). Therefore, the study focuses on these two time lags and evaluate the statistical significance of both. In the following sections, the study examines the statistical significance of those stock market index variables on the vote share of the incumbent government party. Also, the research looked into whether TV broadcasting of stock index has influenced the people's voting behavior. Moreover, since conservative parties tend to more support policies favorable for market than liberal parties, the study scoped into the difference of impacts of stock market index between when the government is conservative and when it is liberal. If interested, the whole paper is avaiable hence please feel free to message me.


